---
title: "results reproduction"
output: html_document
author: "Jocelyn Hu"
---
```{r, eval = FALSE}
library(tidyverse)
library(yardstick)
library(ggplot2)
library(mosaic)
library(stargazer)
require(Stat2Data)
library(scales)
library(readr)
library(rms)
```

```{r}
library(haven)
Dyadic_dta<- read_dta("Data/AttanasioEtAl2011Dyadic.dta")
Dyadic<-read.csv("Dyadic.csv")
Dyadic_mdum<-read.csv("Dyadic_mdum.csv")
```

```{r}
glimpse(Dyadic_dta)
```

```{r}
str(Dyadic)
```

Mutate var stranger which does no exist in the original dataframe 
```{r}
tally(~Dyadic$municode)
tally(~Dyadic$samegroup)
#Dyadic<-na.omit(Dyadic) 
Dyadic<-Dyadic%>%
  mutate(stranger = 1 - as.numeric(Dyadic$frfam))
Dyadic$municode<-as.numeric(Dyadic$municode)
```

```{r}

for (x in 1:70){
name <-paste("mdum",x,sep="")
Dyadic[[name]] <- ifelse(Dyadic$municode == x, 1, 0)
}
```

```{r}
Dyadic<-Dyadic %>% mutate_each(funs(factor), starts_with("mdum"))
class(Dyadic$mdum1)
```

```{r}
pervar<-c("samegroup","friend2","friendfamily","stranger", "frfam","family2", "friend1", "family1", "frfamcl", "difurban", "diffemale","difmarried")
for (i in pervar) {
Dyadic[[i]] <- (as.numeric(Dyadic[[i]]))*100
}

Dyadic[["sumtcons"]] <- (as.numeric(Dyadic[["sumtcons"]]))/1000

Dyadic[["diftcons"]] <- (as.numeric(Dyadic[["diftcons"]]))/1000
```

https://www.princeton.edu/~otorres/NiceOutputR.pdf

The variable difmar's name should be 'difmarried' and nummar should be nummarried.

```{r, message = FALSE}
stargazer(subset(Dyadic[c("samegroup","difchoice1","sumchoice1","frfam","friend2","friendfamily", "family2", "friend1", "family1","stranger","frfamcl", "difurban", "diffemale", "difyage", "difysch", "difmarried","diftcons","difcons", "difhhsize","difwin1","sumurban","sumfemale","sumyage", "sumysch", "nummarried", "sumtcons", "sumcons", "sumhhsize", "sumwin1")],Dyadic$inreg ==1), type = "html", title="Table4: Dyadic Variables", digits=4, out="table4.html", covariate.labels = c("Joined same group in round 2(%)", "Difference in gamble choice(round1)","Sum of gamble choices (round 1)", "Friends and family: One or both recognized friendship or kinship(%)","Both recognized friendship(%)","Both recognized kinship(%)","One recognized friendship, other kinship(%)","One recognized friendship(%)", "One recognized kinship(%)", "Stranger(%)","Geographically proximate friends and family(%)","One lives in the municipal centre, one not(%)","Different genders(%)","Difference in age(years)","Difference in education (years)","Difference in marital status(%)","Difference in household consumption ('000s Pesos/month)","Difference in log household consumption per month","Difference in household size","Difference in round 1 winnings ('000 Pesos)","Number who live in the municipal centre","Number of females","Sum of ages (years)","Sum of education (years)","Number married","Sum of household consumption ('000s Pesos/month)","Sum of log household consumption per month","Sum of household sizes","Sum of round 1 winnings ('000s Pesos)"), summary.stat = c("mean", "sd"))

```

# ```{r}
# stargazer(fixed0,fixed,fixed2,fixed3,fixed4,type = "html", column.labels = c("pumaFixed","pumaRandom","stateFixed","puma","state"), column.separate = NULL,dep.var.labels= "Log(%NativeEduc)",title="Regression Results", covariate.labels=c("Log(%ImmigranNEduct)","Log(%ImmigrantEduc)","Log(%ImmiEng)","Log(AvgWageN)","Log(EmployRateN)","Log(%ImmigrantEduc)*Log(EmployRateN)","Log(%ImmigranNEduct)*Log(EmployRateN)"),align=TRUE, out="models.htm",omit.stat=c("LL","ser","f"),ci=FALSE, ci.level=0.90,no.space=TRUE)



```{r}
pervar<-c("samegroup","friend2","friendfamily","stranger", "frfam","family2", "friend1", "family1", "difurban","frfamcl", "diffemale","difmarried")

for (i in pervar) {
Dyadic[[i]] <- (as.numeric(Dyadic[[i]]))/100
}

```

```{r}
#generate formula for column 1 of table 5
mdum <- Dyadic[, grepl("mdum", names(Dyadic))]
mdumf<-paste(names(mdum),collapse = '+')
c1_formula <- as.formula(paste("samegroup ~ difchoice1+frfamcl+dcfrfamcl+factor(municode)+",mdumf))
print(c1_formula)
```

```{r}
library(glmmML)
# c1 <- glmmboot(samegroup ~ difchoice1+frfamcl+dcfrfamcl, cluster = municode,family = binomial, data = Dyadic)
# c1
c1 <- glm(c1_formula,family = binomial(link="logit"), data = Dyadic)
c1
```
```{r}
coef(c1)
```


```{r}
#marginal effect function
# mfxboot <- function(model,data,dist,boot=1000,digits=3){
#   x <- model
#   # get marginal effects
#   pdf <- ifelse(dist=="probit",
#                 mean(dnorm(predict(x, type = "link"))),
#                 mean(dlogis(predict(x, type = "link"))))
#   marginal.effects <- pdf*coef(x)
#   # start bootstrap
#   bootvals <- matrix(rep(NA,boot*length(coef(x))), nrow=boot)
#   set.seed(1111)
#   for(i in 1:boot){
#     samp1 <- data[sample(1:dim(data)[1],replace=T,dim(data)[1]),]
#     x1 <- glm(modform, family=binomial(link=dist),samp1)
#     pdf1 <- ifelse(dist=="probit",
#                    mean(dnorm(predict(x, type = "link"))),
#                    mean(dlogis(predict(x, type = "link"))))
#     bootvals[i,] <- pdf1*coef(x1)
#   }
#   res <- cbind(marginal.effects,apply(bootvals,2,sd),marginal.effects/apply(bootvals,2,sd))
#   if(names(x$coefficients[1])=="(Intercept)"){
#     res1 <- res[2:nrow(res),]
#     res2 <- matrix(as.numeric(sprintf(paste("%.",paste(digits,"f",sep=""),sep=""),res1)),nrow=dim(res1)[1])
#     rownames(res2) <- rownames(res1)
#   } else {
#     res2 <- matrix(as.numeric(sprintf(paste("%.",paste(digits,"f",sep=""),sep="")),nrow=dim(res)[1]))
#     rownames(res2) <- rownames(res)
#   }
#   colnames(res2) <- c("marginal.effect","standard.error","z.ratio")
#   return(res2)
# }
# mfxboot(c1,"logit",Dyadic,boot=1000,digits=3)
```

```{r}
library("margins")
c1_m<-margins(c1, type = "link",variables = c("difchoice1","frfamcl","dcfrfamcl"))
```


```{r}
summary(c1_m)
```

```{r}
c2_formula <- paste("samegroup ~ difchoice1 +friend2+ friendfamily+ family2 +friend1 +family1+ frfamcl+ dcfrfamcl +difurban +diffemale+ difyage +difysch+ difmarried+ difcons +difhhsize +difwin1 +sumchoice1+ sumurban+ sumfemale +sumyage +sumysch +nummarried +sumcons +sumhhsize +sumwin1 +",mdumf)
print(c2_formula)
c2 <- glmmboot(c2_formula, cluster = municode,family = binomial(link="logit"), data = Dyadic)
c2
mfxboot(c2_formula,"logit",Dyadic,boot=1000,digits=3)
```


```{r}
Dyadic_c3<-Dyadic%>%
  filter(frfamcl==1)
c3_formula <- paste("samegroup ~ difchoice1 + friend2+ friendfamily +family2 +friend1 +difurban +diffemale+ difyage +difysch +difmarried +difcons+ difhhsize +difwin1+ sumchoice1 +sumurban+ sumfemale +sumyage+ sumysch +nummarried +sumcons+ sumhhsize +sumwin1+",mdumf)
print(c3_formula)
c3 <- glmmboot(c3_formula, cluster = municode,family = binomial(link="logit"), data = Dyadic_c3)
c3
mfxboot(c3_formula,"logit",Dyadic,boot=1000,digits=3)
```

```{r}
Dyadic_c4<-Dyadic%>%
  filter(frfamcl==0)
c4_formula <- paste("samegroup ~ difchoice1 + friend2+ friendfamily +family2 +friend1 +family1+difurban +diffemale+ difyage +difysch +difmarried +difcons+ difhhsize +difwin1+ sumchoice1 +sumurban+ sumfemale +sumyage+ sumysch +nummarried +sumcons+ sumhhsize +sumwin1+",mdumf)
print(c4_formula)
c4 <- glmmboot(c4_formula, cluster = municode,family = binomial(link="logit"), data = Dyadic_c4)
c4
mfxboot(c4_formula,"logit",Dyadic,boot=1000,digits=3)
```

